A Data-Driven Framework for Neural Field Modelling

### 2010-11-18 ltx/first_order_framework/LaTeX_Manuscript.tex
edits from proof read of entire paper

\documentclass[5p]{elsarticle}
% \documentclass[12pt]{iopart} 
% \usepackage{iopams}

% % for checking equation size
% % ~~~~~~~~~~~~~~~~~~~~~~~~~~~
% \documentclass[a4paper,10pt,twocolumn]{article} 
% \usepackage{amsmath}
% \usepackage{anysize} %<-use this for checking equation length
% \marginsize {1.6cm}{1.6cm}{1.0cm}{1.8cm} %<-use this for checking equation length
% \setlength{\columnsep}{0.5cm} %<-use this for checking equation length
% % ~~~~~~~~~~~~~~~~~~~~~~~~~~~
\usepackage{amsmath}

@@

\journal{Neuroimage}

\begin{document}

	\begin{frontmatter}
% Title must be 150 characters or less
\title{A Data-Driven Framework for Neural Field Modelling}

\author[DEEE,BEI,UE]{D. R. Freestone\corref{cor1}}
\ead{dfreestone@bionicear.org}
\author[US]{P. Aram} 
\author[UE,CU]{M. Dewar}
\author[UM]{K. Scerri}
\author[DEEE,BEI]{D. B. Grayden}
\author[US]{V. Kadirkamanathan}

\address[DEEE]{Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC, Australia}
\address[BEI]{The Bionic Ear Institute, East Melbourne, VIC, Australia}
\address[UE]{Institute for Adaptive and Neural Computation, University of Edinburgh, Edinburgh, UK}
\address[US]{Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, UK}
\address[CU]{Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA}
\address[UM]{Department of Systems and Control Engineering, University of Malta, Msida, MSD, Malta}

\begin{abstract}
This paper presents a framework for creating neural field models from electrophysiological data. The Wilson and Cowan or Amari style neural field equations are used to form a parametric model, where the parameters are estimated from data. To illustrate the estimation framework, data is generated using the neural field equations incorporating modelled sensors so a comparison can be made between estimated and true parameters. To facilitate state and parameter estimation, we introduce a method to reduce the continuum neural field model using a basis function decomposition to form a finite-dimensional state-space model. Spatial frequency analysis methods are introduced that systematically specify the basis function configuration required to capture the dominant characteristics of the neural field. The estimation procedure consists of a two-stage iterative algorithm incorporating the unscented Rauch-Tung-Striebel smoother for state estimation and a least squares algorithm for parameter estimation. The results show that it is theoretically possible to reconstruct the neural field and estimate intracortical connectivity structure and synaptic dynamics with the proposed framework. %The results also illustrate a systematic loss of high spatial frequency information as the cost incurred by the model reduction procedure. 
\end{abstract}

\begin{keyword}
	keyword1 \sep keyword2
%% keywords here, in the form: keyword \sep keyword

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

@@

\begin{align}

@@

	\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1} &= T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}') \, d\mathbf{r}'}\boldsymbol{\theta} \nonumber \\
	&+ \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + \mathbf{e}_t(\mathbf{r}). 
\end{align}

@@

 	\int_\Omega \boldsymbol{\phi} &\left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right)d\mathbf{r} \mathbf{x}_{t+1}  \nonumber \\
 &=T_s \int_\Omega \boldsymbol{\phi} (\mathbf{r}) \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}') 
 f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) \, d\mathbf{r}'d\mathbf{r}\boldsymbol{\theta} \nonumber \\ 
&+ \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t + 

@@

\end{align}

@@

	 \mathbf{x}_{t+1} &= T_s\boldsymbol{\Gamma}^{-1}

@@

	 \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t)d\mathbf{r}' d\mathbf{r} \boldsymbol{\theta}  \nonumber \\
	& + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r}) e_t(\mathbf{r}) \, d\mathbf{r}}.
\end{align}

@@

\begin{align}
	\mathbf{x}_{t+1} &= \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \, d\mathbf{r}' \boldsymbol{\theta} \nonumber \\ &+ \xi\mathbf{x}_t 

@@

The unscented Rauch-Tung-Striebel smoother (URTSS)~\cite{Sarkka2010} is used for the state estimation. The URTSS incorporates an unscented Kalman filter (UKF)~\cite{Julier1997, Merwe2003} in a forward step to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward step to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$. The first and second order moments of the predicted state are captured by propagating the so-called sigma points through the state equation. The sigma points, $\mathcal X_i$, are calculated using the unscented transform as follows:
\begin{align}\label{eq:sigmapoints1}
	\mathcal X_{0}&=\bar x \\
	\mathcal X_{i}&=\bar x+\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_i, \quad i=1, \dots, n_x \\
	\mathcal X_{i}&=\bar x-\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_{i- n_x}, \quad i= n_x+1, \dots, 2n_x 
\end{align}
where $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix for filtering or smoothing, $\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_i$ is the $i^{th}$ column of the scaled matrix square root of $\mathbf P_x$, and $n_x$ is the dimension of the state space. The total number of sigma points is $2n_x+1$. The scaling parameter, $\lambda$, is defined as 
\begin{equation}\label{eq:sigmapoints3}
	\lambda=\alpha^2( n_x+\kappa) - n_x, 
\end{equation}
where the constant $\alpha$ determines the spread of the sigma points and $\kappa$ is an additional scaling parameter (see~\cite{Haykin2001} for more details).

The sigma vectors are propagated through the system equations and weighted to form the predicted mean and covariance. The weights are calculated by 
\begin{align}
	\mathbf W_0^{(m)}&=\frac{\lambda}{ n_x+\lambda} \\
	\mathbf W_0^{(c)}&=\frac{\lambda}{ n_x+\lambda}+(1-\alpha^2+\beta) \\
	\mathbf W_i^{(m)}&=\mathbf W_i^{(c)}=\frac{1}{2( n_x+\lambda)} \quad i=1, \dots, 2n_x, 
\end{align}
where the superscripts $m$ and $c$ denote mean and covariance and $\beta$ incorporates prior knowledge of the distribution of the states, $\mathbf{x}$. Since the observation equation is linear (equation~\ref{ObservationEquation}), the standard Kalman Filter update equations are used to correct the predicted states. The state estimates from forward filtering are used to form a new set of sigma points for the smoother, as described above. The cross-covariance matrix of the states, $\mathbf M$, is also required for computing the smoother gain, as described in the summary of the steps in the URTSS algorithm is given in Table~\ref{tab:UKFAlgorithm}. It should be noted that the disturbance, $\mathbf{e}_t$, and the measurement noise, $\boldsymbol{\varepsilon}_t$, are additive. Therefore, the additive form of the URTSS is used.

Although the system is nonlinear, the parameters of the system are linear with respect to the state. This is exploited by our procedure where the parameter estimation uses a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new estimate of the state vector sequence. To create the least squares parameter estimator, we first define the $n_x \times n_{\theta}$ matrix
\begin{equation}
	\mathbf{q}(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \,\textrm{d}\mathbf{r}'.
\end{equation}
Now given a state estimate sequence from the initialisation or an iteration of the URTSS, we can write
\begin{align*}
	 \hat{\mathbf x}^b_{1} &= \mathbf{q}(\hat{\mathbf x}^b_0) \boldsymbol{\theta}+\xi\hat{\mathbf x}^b_0+\mathbf e_0 \\
	\hat{\mathbf x}^b_{2} &= \mathbf{q}(\hat{\mathbf x}^b_1) \boldsymbol{\theta}+\xi\hat{\mathbf x}^b_1+\mathbf e_1  \\
	&\vdots& \\
	\hat{\mathbf x}^b_{T}&= \mathbf{q}(\hat{\mathbf x}^b_{T-1}) \boldsymbol{\theta}+\xi\hat{\mathbf x}^b_{T-1}+\mathbf e_{T-1}. 
\end{align*}
This can be written in the compact form
\begin{equation}
	\mathbf Z=\mathbf X \mathcal W+\mathbf{e}, 
\end{equation}
where
\begin{small}
\begin{equation*}
	\mathbf Z=\left[
	\begin{array}{cccc}
		\hat{\mathbf x}^b_{1}\\
		\hat{\mathbf x}^b_{2}\\
		\vdots\\
		\hat{\mathbf x}^b_{T}
	\end{array}
	\right],\quad \mathbf X=\left[
	\begin{array}{cccc}
		\mathbf q(\hat{\mathbf x}^b_0)& \hat{\mathbf x}^b_{0}\\
		\mathbf q(\hat{\mathbf x}^b_1)& \hat{\mathbf x}^b_{1}\\
		\vdots & \vdots\\
		\mathbf q(\hat{\mathbf x}^b_{T-1})& \hat{\mathbf x}^b_{T-1}
	\end{array}
	\right] 
\end{equation*}
\end{small}
and
\begin{small}
\begin{equation*}
\quad \mathcal W=\left[
	\begin{array}{cc}
		\boldsymbol{\theta} \\
		\xi
	\end{array}
	\right],\quad \mathbf{e}=\left[
	\begin{array}{cccc}
		\mathbf e_0\\
		\mathbf e_1\\
		\vdots\\
		\mathbf e_{T-1}
	\end{array}
	\right].
\end{equation*}
\end{small}
Following this, the LS parameter estimates~\cite{Kailath2000}, $ \hat{\mathcal{W}}$, are
\begin{equation}
	\hat{\mathcal{W}}=(\mathbf X^\top\mathbf X)^{-1}\mathbf X^\top\mathbf Z. 
\end{equation}

@@

\ken{revised new bit}

To reduce the computational demand of the estimation procedure, the neural field cutoff frequency was further reduced to $\boldsymbol{\nu}_{c\phi} = 0.12$~Hz. Due to the slow frequency roll-off of Gaussian basis functions an oversampling parameter of $\rho_{\phi} = 1.67$ was chosen. Therefore for an equally spaced grid of basis functions over the full spatial domain being considered, a $9\times9$ grid was required to decompose the field, which resulted in $81$ states. The other parameter of the basis functions, $\sigma_{\phi}^2$, is set based on equation \ref{eq:CutoffFromBasisFuncWidth} and the chosen neural field bandwidth $\boldsymbol{\nu}_{c\phi}$, to give $\sigma_{\phi}^2=2.5$.

\ken{how's that?}

@@

Histograms of the parameter estimates obtained over the 150 realisations are shown in Figure~\ref{fig:Figure7}. In each of the subplots of the figure the true parameter value is shown by the solid line and the mean parameter estimate is shown by the dashed line. The actual parameter values, the mean parameter estimates, standard deviations, and biases for this parameter combination are given as the first entry in Table~\ref{tab:MexicanHatKernelResults}, where other entries in the table show results from Experiment II. The biases show the percentage differences between the actual values and the mean parameter estimates. For this parameter combination the mean estimates are in good agreement (within 1 standard deviation) with the actual values of the connectivity kernel parameters. However, the time constant parameter, $\xi$, is outside the estimate distribution (with bias of $2.56\%$), with a small variance in parameter estimates. We attribute this small bias to the loss of the high frequency components in the smoother estimated field with respect to the actual field. These results thus indicate that choosing to limit the frequency content of the reconstructed neural field has only minor effects on the accuracy of the estimated kernel while allowing for significant gains in the computational demand.

The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over iterations) of the root mean square error (MRMSE) over space. The MRMSE of the field estimates over time for 150 realisations is shown in Figure~\ref{fig:Figure9} with the $95~\%$ confidence interval. At each time point, the error is consistently around $0.5$~mV, which is approximately $10.73~\%$ of the field voltage range ([-2.20, 2.46]~mV). The error in the reconstructed field is again mostly due to the loss of high spatial frequency information from the basis function decomposition as illustrated in Figure~\ref{fig:Figure10}. The figure shows a snapshot at a single time instant of the true neural field, the estimated field, and the corresponding error, which is the difference between the true and estimated neural fields. It can be seen in Figure~\ref{fig:Figure10}(B) that the estimated field contains the basic structure of the true field, shown in Figure~\ref{fig:Figure10}(A), but is missing the higher-frequency detail, which can be see in the error shown in Figure~\ref{fig:Figure10}(C).

@@

For each of the Mexican hat connectivities, the support of the kernel was assumed to be known. However, in Figure~\ref{fig:Figure8}(D-F) the kernel support in the estimator differed from the actual data. In these cases the data sets were generated using a single positive (excitatory) Gaussian kernel, as seen by the solid line in each of the subplots of the figure. The estimation algorithm was constructed allowing for the Mexican hat connectivity of the previous examples. Each plot shows that the actual kernel lies within the confidence intervals of the reconstructed estimates for the majority of the kernel space, until the amplitude is relatively low. Table~\ref{tab:GaussianKernelResults} shows the statistics of the parameter estimates. Although the net reconstructed kernel estimates are in good accord with the actual kernels, the individual kernel basis function weights are not in agreement with the actual parameters. This result demonstrates that unless the widths of the Gaussians forming the kernel are precisely known, the interpretation of the results should be based on the net shape of the estimated connectivity kernel and not on the estimated parameter values individually.

@@

% The size of the squares in the figure show the magnitude of the log of the error. The squares are black if the log of the error is negative (the RMSE is $<1$) and the squares are white if the log of the error is positive (the RMSE is $>1$). The largest black squares indicate the best performance and the largest white squares indicate the worst performance for the parameter combinations (\dean{need some thing more quantitative}). 
From Figure~\ref{fig:Figure12} it can be seen that the estimation accuracy depends on the parameters of the sigmoid function. This is expected since by altering the parameters we are changing the nonlinearity and the saturation region of the sigmoid.

\ken{what I would write}

For example, when the sigmoid slope is very gentle, most of the neural activity falls in the central, nearly linear region of the sigmoid, thus having minor effects on the estimation procedure. On the other hand, sharp slopes result in most of the activity falling in the saturation region of the sigmoid with adverse effects on the estimation. Similar arguments can be made for variations to the sigmoid threshold.

\ken{what do you think?}

\dean{PLEASE HELP TO FILL THIS SECTION IN. ANYTHING WILL DO.}
..\dean{This next bit is CRAP (please help):} When the threshold is negative or the slope is very gentle, all of the activity is being passed through the sigmoid function. However, as the slope is increased or the threshold is increased, more of the field is within the saturating region of the activation function. This is illustrated in Figure~\ref{fig:sigmoidfunctions}, where the sigmoids from the bottom left corner through to near top right corner of Figure~\ref{fig:sigmoidfunctions} are plotted. This appears to have a detrimental effect on the estimation accuracy.

\subsubsection{Experiment IV: Results for Varying the Sensor Kernel Width}
The accuracy of the estimation algorithm was tested for different observation kernels by varying the width parameter, $\sigma_m$. Figure~\ref{fig:Figure13} shows the RMSE of the connectivity kernel estimates for the various observation kernel widths. As the theory presented earlier in Section~\ref{SpectralAnalysisSection} suggests, the observation kernel acts as a spatial filter.

\ken{tried to make it a little more straight forward}

When the observation kernel is too narrow, high frequency components in the neural field are sampled. These high frequency components result in aliasing errors in the estimated field thus affecting the kernel estimation accuracy. On the other hand, for the very wide kernels considered, important neural dynamics are not pick up by the estimated field due to the filtering out of the high frequency components by the sensors, resulting in poor accuracy in the kernel estimate. Thus, as indicated in Figure~\ref{fig:Figure13}, the best results are obtained when the sensor width is chosen to minimize both sources of errors.

\ken{that ok?}

When the observation kernel is too narrow, a small amount of high spatial frequency information is still present but not adequately sampled by the observation function, since the field is not exactly band-limited. Therefore, a small amount of aliasing occurs which results in the estimation error. When the observation kernel width is increased, the high spatial frequency information that is not adequately sampled is filtered more strongly by the observation kernel and the error decreases. However, as expected when the observation kernel becomes too large, important spatial frequency information is lost and the error becomes larger.

\section{Discussion}\label{DiscussionSection}

@@

\section{Conclusion}
\dean{I MOVED THIS FROM THE START OF THE DISCUSSION. ANY OBJECTIONS?} This paper has presented a framework for creating data-driven neural field models by developing a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data. In doing so, we have highlighted important aspects of the experiment design process, demonstrating the relationship between sensor bandwidth and the complexity of the field that can be inferred. We have derived a finite-order state-space representation of the continuum neural field equations that allows inference to be performed efficiently. Importantly, the mathematical formulation that we have presented scales well with the number of sensors. The major contribution of this framework is to formally bridge a gap between experimental and theoretical neuroscience in order to gain a better understanding of the mesoscopic dynamics of the brain.

>>>>

\documentclass[12pt]{iopart} 
\usepackage{iopams}

% % for checking equation size
% % ~~~~~~~~~~~~~~~~~~~~~~~~~~~
% \documentclass[a4paper,10pt,twocolumn]{article} 
% \usepackage{amsmath}
% \usepackage{anysize} %<-use this for checking equation length
% \marginsize {1.6cm}{1.6cm}{1.0cm}{1.8cm} %<-use this for checking equation length
% \setlength{\columnsep}{0.5cm} %<-use this for checking equation length
% % ~~~~~~~~~~~~~~~~~~~~~~~~~~~

@@

\begin{document}
% Title must be 150 characters or less
\title[A Data-Driven Framework for Neural Field Modelling]{A Data-Driven Framework for Neural Field Modelling}

\author{Dean R. Freestone$^{1,2,3}$, 
Parham Aram$^{4}$, 
Michael Dewar$^{3,5}$,
Kenneth Scerri$^{6}$,
David B. Grayden$^{1,2}$,
Visakan Kadirkamanathan$^{4}$}

\address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC, Australia
\\
$^2$ The Bionic Ear Institute, East Melbourne, VIC, Australia
\\
$^3$ Institute for Adaptive and Neural Computation, University of Edinburgh, Edinburgh, UK
\\
$^4$ Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, UK
\\
$^5$ Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA
\\
$^6$ Department of Systems and Control Engineering, University of Malta, Msida, MSD, Malta}

\ead{dfreestone@bionicear.org}

\begin{abstract}
This paper presents a framework for creating neural field models from electrophysiological data. The Wilson and Cowan or Amari style neural field equations are used to form a parametric model, where the parameters are estimated from data. To illustrate the estimation framework, data is generated using the neural field equations incorporating modelled sensors so a comparison can be made between estimated and true parameters. To facilitate state and parameter estimation, we introduce a method to reduce the continuum neural field model using a basis function decomposition to form a finite-dimensional state-space model. Spatial frequency analysis methods are introduced that systematically specify the basis function configuration required to capture the dominant characteristics of the neural field. The estimation procedure consists of a two-stage iterative algorithm incorporating the unscented Rauch-Tung-Striebel smoother for state estimation and a least squares algorithm for parameter estimation. The results show that it is theoretically possible to reconstruct the neural field and estimate intracortical connectivity \parham{kernel} and synaptic dynamics with the proposed framework. %The results also illustrate a systematic loss of high spatial frequency information as the cost incurred by the model reduction procedure. 
\end{abstract}

\maketitle

@@

\begin{eqnarray}

@@

	\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1} &=& T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}') \, d\mathbf{r}'}\boldsymbol{\theta} \nonumber \\
	&+& \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + \mathbf{e}_t(\mathbf{r}). 
\end{eqnarray}

@@

 	\int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} &=&
 T_s \int_\Omega \boldsymbol{\phi} (\mathbf{r}) \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}') \nonumber \\
&\times& { f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) \, d\mathbf{r}'d\mathbf{r}}\boldsymbol{\theta} \nonumber \\ 
&+& \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \nonumber \\ &+& 

@@

\end{eqnarray}

@@

    % \begin{split}
	 \mathbf{x}_{t+1} &=& T_s\boldsymbol{\Gamma}^{-1}

@@

	 \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \nonumber \\
	&\times& d\mathbf{r}' d\mathbf{r} \boldsymbol{\theta}  
	 + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r}) e_t(\mathbf{r}) \, d\mathbf{r}}.
	 % \end{split}
\end{eqnarray}

@@

\begin{eqnarray}
	\mathbf{x}_{t+1} &=& \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \, d\mathbf{r}' \boldsymbol{\theta} \nonumber \\ &+& \xi\mathbf{x}_t 

@@

The unscented Rauch-Tung-Striebel smoother (URTSS)~\cite{Sarkka2010} is used for the state estimation. The URTSS incorporates an unscented Kalman filter (UKF)~\cite{Julier1997, Merwe2003} in a forward step to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward step to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$. The first and second order moments of the predicted state are captured by propagating the so-called sigma points through the state equation. The sigma points, $\mathcal X_i$, are calculated using the unscented transform as follows:
\begin{eqnarray}\label{eq:sigmapoints1}
	\mathcal X_{0}&=&\bar x \\
	\mathcal X_{i}&=&\bar x+\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_i, \quad i=1, \dots, n_x \\
	\mathcal X_{i}&=&\bar x-\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_{i- n_x}, \quad i= n_x+1, \dots, 2n_x 
\end{eqnarray}
where $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix for filtering or smoothing, $\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_i$ is the $i^{th}$ column of the scaled matrix square root of $\mathbf P_x$, and $n_x$ is the dimension of the state space. The total number of sigma points is $2n_x+1$. The scaling parameter, $\lambda$, is defined as 
\begin{equation}\label{eq:sigmapoints3}
	\lambda=\alpha^2( n_x+\kappa) - n_x, 
\end{equation}
where the constant $\alpha$ determines the spread of the sigma points and $\kappa$ is an additional scaling parameter (see~\cite{Haykin2001} for more details).

The sigma vectors are propagated through the system equations and weighted to form the predicted mean and covariance. The weights are calculated by 
\begin{eqnarray}
	\mathbf W_0^{(m)}&=&\frac{\lambda}{ n_x+\lambda} \\
	\mathbf W_0^{(c)}&=&\frac{\lambda}{ n_x+\lambda}+(1-\alpha^2+\beta) \\
	\mathbf W_i^{(m)}&=&\mathbf W_i^{(c)}=\frac{1}{2( n_x+\lambda)} \quad i=1, \dots, 2n_x, 
\end{eqnarray}
where the superscripts $m$ and $c$ denote mean and covariance and $\beta$ incorporates prior knowledge of the distribution of the states, $\mathbf{x}$. Since the observation equation is linear (equation~\ref{ObservationEquation}), the standard Kalman Filter update equations are used to correct the predicted states. The state estimates from forward filtering are used to form a new set of sigma points for the smoother, as described above. The cross-covariance matrix of the states, $\mathbf M$, is also required for computing the smoother gain, as described in the summary of the steps in the URTSS algorithm is given in Table~\ref{tab:UKFAlgorithm}. It should be noted that the disturbance, $\mathbf{e}_t$, and the measurement noise, $\boldsymbol{\varepsilon}_t$, are additive. Therefore, the additive form of the URTSS is used.

Although the system is nonlinear, the parameters of the system are linear with respect to the state. This is exploited by our procedure where the parameter estimation uses a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new estimate of the state vector sequence. To create the least squares parameter estimator, we first define the $n_x \times n_{\theta}$ matrix
\begin{equation}
	\mathbf{q}(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \,\textrm{d}\mathbf{r}'.
\end{equation}
Now given a state estimate sequence from the initialisation or an iteration of the URTSS, we can write
\begin{eqnarray*}
	 \hat{\mathbf x}^b_{1} &=& \mathbf{q}(\hat{\mathbf x}^b_0) \boldsymbol{\theta}+\xi\hat{\mathbf x}^b_0+\mathbf e_0 \\
	\hat{\mathbf x}^b_{2} &=& \mathbf{q}(\hat{\mathbf x}^b_1) \boldsymbol{\theta}+\xi\hat{\mathbf x}^b_1+\mathbf e_1  \\
	&\vdots& \\
	\hat{\mathbf x}^b_{T}&=& \mathbf{q}(\hat{\mathbf x}^b_{T-1}) \boldsymbol{\theta}+\xi\hat{\mathbf x}^b_{T-1}+\mathbf e_{T-1}. 
\end{eqnarray*}
This can be written in the compact form
\begin{equation}
	\mathbf Z=\mathbf X \mathcal W+\mathbf{e}, 
\end{equation}
where
\begin{small}
\begin{equation*}
	\mathbf Z=\left[
	\begin{array}{cccc}
		\hat{\mathbf x}^b_{1}\\
		\hat{\mathbf x}^b_{2}\\
		\vdots\\
		\hat{\mathbf x}^b_{T}
	\end{array}
	\right],\quad \mathbf X=\left[
	\begin{array}{cccc}
		\mathbf q(\hat{\mathbf x}^b_0)& \hat{\mathbf x}^b_{0}\\
		\mathbf q(\hat{\mathbf x}^b_1)& \hat{\mathbf x}^b_{1}\\
		\vdots & \vdots\\
		\mathbf q(\hat{\mathbf x}^b_{T-1})& \hat{\mathbf x}^b_{T-1}
	\end{array}
	\right] 
\end{equation*}
\end{small}
and
\begin{small}
\begin{equation*}
\quad \mathcal W=\left[
	\begin{array}{cc}
		\boldsymbol{\theta} \\
		\xi
	\end{array}
	\right],\quad \mathbf{e}=\left[
	\begin{array}{cccc}
		\mathbf e_0\\
		\mathbf e_1\\
		\vdots\\
		\mathbf e_{T-1}
	\end{array}
	\right].
\end{equation*}
\end{small}
Following this, the LS parameter estimates~\cite{Kailath2000}, $ \hat{\mathcal{W}}$, are
\begin{equation}
	\hat{\mathcal{W}}=(\mathbf X^\top\mathbf X)^{-1}\mathbf X^\top\mathbf Z. 
\end{equation}

@@

\ken{revise}

@@

Histograms of the parameter estimates obtained over the 150 realisations are shown in Figure~\ref{fig:Figure7}. In each of the subplots of the figure the true parameter value is shown by the solid line and the mean parameter estimate is shown by the dashed line. The actual parameter values, the mean parameter estimates, standard deviations, and biases for this parameter combination are given as the first entry in Table~\ref{tab:MexicanHatKernelResults}, where other entries in the table show results from Experiment II. The biases show the percentage differences between the actual values and the mean parameter estimates. For this parameter combination the mean estimates are in good agreement (within 1 standard deviation) with the actual values of the connectivity kernel parameters. However, the time constant parameter, $\xi$, is outside the estimate distribution (with bias of $2.56\%$), with a small variance in parameter estimates. We attribute this small bias to the disparity between the actual field and the smoother estimated field from the decomposition.

The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over iterations) of the root mean square error (MRMSE) over space. The MRMSE of the field estimates over time for 150 realisations is shown in Figure~\ref{fig:Figure9} with the $95~\%$ confidence interval. At each time point, the error is consistently around $0.5$~mV, which is approximately $10.73~\%$ of the field voltage range ([-2.20, 2.46]~mV). The error in the reconstructed field is mostly due to the loss of high spatial frequency information from the basis function decomposition as illustrated in Figure~\ref{fig:Figure10}. The figure shows a snapshot at a single time instant of the true neural field, the estimated field, and the corresponding error, which is the difference between the true and estimated neural fields. It can be seen in Figure~\ref{fig:Figure10}(B) that the estimated field contains the basic structure of the true field, shown in Figure~\ref{fig:Figure10}(A), but is missing the higher-frequency detail, which can be see in the error shown in Figure~\ref{fig:Figure10}(C).

@@

For each of the Mexican hat connectivities, the support of the kernel was assumed to be known. However, in Figure~\ref{fig:Figure8}(D-F) the kernel support in the estimator differed from the actual data. In these cases the data sets were generated using a single positive (excitatory) Gaussian kernel, as seen by the solid line in each of the subplots of the figure. The estimation algorithm was constructed allowing for the Mexican hat connectivity of the previous examples. Each plot shows that the actual kernel lies within the confidence intervals of the reconstructed estimates for the majority of the kernel space, until the amplitude is relatively low. Table~\ref{tab:GaussianKernelResults} shows the statistics of the parameter estimates. Although the net reconstructed kernel estimates are in good accord with the actual kernels, the individual kernel basis function weights are not in agreement with the actual parameters. This result demonstrates that unless the support of the kernel is precisely known, the interpretation of the results should be based on the net shape of the estimated connectivity kernel and not on the estimated parameter values individually.

@@

% The size of the squares in the figure show the magnitude of the log of the error. The squares are black if the log of the error is negative (the RMSE is $<1$) and the squares are white if the log of the error is positive (the RMSE is $>1$). The largest black squares indicate the best performance and the largest white squares indicate the worst performance for the parameter combinations (\dean{need some thing more quantitative}). 
From Figure~\ref{fig:Figure12} it can be seen that the estimation accuracy depends on the parameters of the sigmoid function. This is expected since that by altering the parameters we are changing the nonlinearity and the saturation region of the sigmoid.  
\dean{PLEASE HELP TO FILL THIS SECTION IN. ANYTHING WILL DO.}
..\dean{This next bit is CRAP (please help):} When the threshold is negative or the slope is very gentle, all of the activity is being passed through the sigmoid function. However, as the slope is increased or the threshold is increased, more of the field is within the saturating region of the activation function. This is illustrated in Figure~\ref{fig:sigmoidfunctions}, where the sigmoids from the bottom left corner through to near top right corner of Figure~\ref{fig:sigmoidfunctions} are plotted. This appears to have a detrimental effect on the estimation accuracy.

\subsubsection{Experiment IV: Results for Varying the Sensor Kernel Width}
The accuracy of the estimation algorithm was tested for different observation kernels by varying the width parameter, $\sigma_m$. Figure~\ref{fig:Figure13} shows the RMSE of the connectivity kernel estimates for the various observation kernel widths. As the theory presented earlier in Section~\ref{SpectralAnalysisSection} suggests, the observation kernel acts as a spatial filter. When the observation kernel is too narrow, a small amount of high spatial frequency information is still present but not adequately sampled by the observation function, since the field is not exactly band-limited. Therefore, a small amount of aliasing occurs which results in the estimation error. When the observation kernel width is increased, the high spatial frequency information that is not adequately sampled is filtered more strongly by the observation kernel and the error decreases. However, as expected when the observation kernel becomes too large, important spatial frequency information is lost and the error becomes larger.

\section{Discussion}\label{DiscussionSection}
This paper has presented a framework for creating data-driven neural field models by developing a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data. In doing so, we have highlighted important aspects of the experiment design process, demonstrating the relationship between sensor bandwidth and the complexity of the field that can be inferred. We have derived a finite-order state-space representation of the neural field equations that allows us to perform inference efficiently and the mathematical formulation that we have presented scales well with the number of sensors.

@@

\section{Conclusion}
This paper has made a contribution to bridging the gap between experimental and theoretical neuroscience by developing a systematic methodology. \dean{Please add to this.} Novel aspects of this work include a model reduction procedure such that a finite-dimension state-space model constructed... \dean{PLEASE HELP TO FILL THIS SECTION IN. ANYTHING WILL DO.}
